---
title: "HW03 template"
output:
  word_document: default
  pdf_document: default
  
  ### Name
---

```{r setup, include=FALSE}

library(car)
library(agricolae)
library(DunnettTests)
library(multcomp)

```

**Problem**
An agronomist was interested in testing the impact of planting date on the biomass and nitrogen uptake of a winter rye cover crop. To this end, five planting dates were explored at a location in on the US/Canada border. In addition to biomass, growth stage of the rye, the nitrogen uptake and the number of growing degree days were also assessed. The design was a randomized complete block with four replications. 

**a.	State the null and alternative hypotheses for the experiment.**
**Answer:** 
Null Hypothesis: 
Alternative Hypothesis: 

**b. Write the linear model and define the components of the model.**
**recal this is the abstraction of the design**
**Answer:** 



**c.	Conduct an Analysis of Variance (ANOVA) for for two of the response variables**
```{r}
cc<- read.csv('') #read in data
head(cc)
str(cc)
aov.cc <- aov()

```

**d.	Write out the table**
```{r}
summary(aov.cc)
```


**e. Construct a table of treatment means using an appropriate mean separation procedure of your choice.**

```{r}

lsd.cc <- LSD.test() # or HSD or dunnett
bar.group()
title(cex.main=0.8,main="Impact of Planting date Yield",xlab="Planting Date",ylab="Yield")

```

**f.	Write a brief summary of the results and discuss conclusions you could draw from the data set.**
**Answer:** 








## R Markdown

